**Credit Risk Distribution and Capital Savings**

### 2020-01-07 docs/poster/poster.Rmd
change folder of poster to docs

source("../Auxiliar/Function.R") ## Capital requirements functions

@@

```{r load data, include=TRUE}
load("../Data/Datasets/Pillar3Data.Rda")
load("../Data/Datasets/BankData.Rda")
load("../Data/Datasets/CrossSectionDecomposition.Rda")
load("../Data/Datasets/timedecomposition.Rda")
load("../Data/Datasets/yeardecomposition.Rda")
```

>>>>

source("../../Auxiliar/Function.R") ## Capital requirements functions

@@

```{r load data, include=TRUE}
load("../../Data/Datasets/Pillar3Data.Rda")
load("../../Data/Datasets/BankData.Rda")
load("../../Data/Datasets/CrossSectionDecomposition.Rda")
load("../../Data/Datasets/timedecomposition.Rda")
load("../../Data/Datasets/yeardecomposition.Rda")
```
